**Seasonal Dynamics of Epiphytic Microbial Communities on Marine Macrophyte Surfaces**

### 2020-05-28 submission/manuscript.Rmd
Review optimization.

We observed a strong differentiation between the surface attached and ambient seawater communities at the level of OTUs, in agreement with most published studies [@Ugarelli2019; @Roth-Schulze2016; @Burke2011a; @Michelou2013; @Crump2018; @Mancuso2016]. This indicates that marine macrophytes are a selecting factor from the pool of microbial taxa present in the ambient seawater, modifying the microbial community once the macrophyte associated microbial biofilm develops [@Salaun2012; @Michelou2013]. In contrast, @Fahimipour2017 report in a global study of *Zostera marina*, similarities between the microbial community developed on leaves and in the ambient seawater. The discrepancy between our data and the study of @Fahimipour2017 could be explained by different seagrass species, methodological variations or biogeographic trends as @Fahimipour2017 analyzed samples from different locations throughout the northern hemisphere. It is possible that the microbial communities in ambient seawater and on leaves from the same location are differing but are still more similar to each other when compared to other sampling locations. Indeed, it was found that prokaryotic communities vary substantially between different sampling sites [@Bengtsson2017]. When the taxonomic composition at high ranks was analyzed no such strong differentiation was noticed. Phyla and classes such as *Actinobacteriota*, *Bacteroidota*, *Cyanobacteria*, *Alphaproteobacteria*, *Gammaproteobacteria* and *Verrucomicrobiota* were found in both ambient seawater as well as macrophyte associated, in agreement with previous studies [@Egan2013; @Michelou2013; @Burke2011a]. In contrast, when low taxonomic ranks were analyzed (i.e., family and genus) a strong differentiation was observed (Figs. \ref{cyano} -- \ref{desulfo}). A similar differentiation at lower microbial taxonomic ranks between ambient seawater and macrophytes was described for other macrophyte species as well [@Egan2013; @Michelou2013; @Ugarelli2019; @Mancuso2016].

>>>>

We observed a strong differentiation between the surface attached and ambient seawater communities at the level of OTUs, in agreement with most published studies [@Ugarelli2019; @Roth-Schulze2016; @Burke2011a; @Michelou2013; @Crump2018; @Mancuso2016]. This indicates that marine macrophytes are a selecting factor from the pool of microbial taxa present in the ambient seawater, modifying the microbial community once the macrophyte associated microbial biofilm develops [@Salaun2012; @Michelou2013]. In contrast, @Fahimipour2017 report in a global study of *Zostera marina*, similarities between the microbial community developed on leaves and in the ambient seawater. The discrepancy between our data and the study of @Fahimipour2017 could be explained by different seagrass species, methodological variations or biogeographic trends as @Fahimipour2017 analyzed samples from different locations throughout the northern hemisphere. It is possible that the microbial communities in ambient seawater and on leaves from the same location are differing but are still more similar to each other when compared to other sampling locations. Indeed, it was found that prokaryotic communities vary substantially between different sampling sites [@Bengtsson2017]. When the taxonomic composition at high ranks was analyzed no such strong differentiation was noticed. Phyla and classes such as *Actinobacteriota*, *Bacteroidota*, *Cyanobacteria*, *Alphaproteobacteria*, *Gammaproteobacteria* and *Verrucomicrobiota* were found in both ambient seawater as well as macrophyte associated, in agreement with previous studies [@Egan2013; @Michelou2013; @Burke2011a]. In contrast, when low taxonomic ranks were analyzed (i.e., family and genus) a strong differentiation was observed (Figs. \ref{cyano} -- \ref{desulfo}). A similar differentiation at lower microbial taxonomic ranks between ambient seawater and macrophytes was described for other macrophyte species as well [@Egan2013; @Michelou2013; @Ugarelli2019].
